---
title: "2: Data Visualization - https://r4ds.hadley.nz/data-visualize"
author: "George C"
date: "2023-10-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 2 Data visualization

## Introduction

### 2.1.1 Prerequisites

```{r}
# install.packages("tidyverse")
library(tidyverse)
library(ggplot2)
library(scales)
library(ggthemes)
```

## 2.2 First steps

### 2.2.1 The penguins data frame


```{r}
penguins <- palmerpenguins::penguins
glimpse(penguins)
```
- Para aprender mais sobre esses dados:
```{r}
?penguins
```

### 2.2.2 Ultimate goal
### 2.2.3 Creating a ggplot
```{r}
# ggplot(data=penguins)

# ggplot(
#  data = penguins,
#  mapping = aes(x=flipper_length_mm, y=body_mass_g))

ggplot(
  data = penguins,
  mapping = aes(x=flipper_length_mm, y=body_mass_g)
) +
  geom_point()
```
### 2.2.4 Adding aesthetics and layers
```{r}
#ggplot(
#  data=penguins,
#  mapping=aes(x=flipper_length_mm, y=body_mass_g, color=species)
#) + 
#  geom_point()

#ggplot(
#  data=penguins,
#  mapping=aes(x=flipper_length_mm, y=body_mass_g, color=species)
#) +
#  geom_point() +
#  geom_smooth(method="lm")

#ggplot(
#  data=penguins,
#  mapping=aes(x=flipper_length_mm, y=body_mass_g)
#) +
#  geom_point(mapping=aes(color=species)) +
#  geom_smooth(method="lm")

#ggplot(
#  data=penguins,
#  mapping=aes(x=flipper_length_mm, y=body_mass_g)
#) +
#  geom_point(mapping=aes(color=species, shape=species)) +
#  geom_smooth(method="lm")

ggplot(
  data=penguins,
  mapping=aes(x=flipper_length_mm, y=body_mass_g)
) +
  geom_point(aes(color=species, shape=species)) +
  geom_smooth(method="lm") +
  labs(
    title="Body mass and flipper length",
    subtitle="Dimensions for Adelie, Chinstrap, and Gentoo Penguins",
    x="Flipper length (mm)", y="Body mass (g)",
    color="Species", shape="Species"
  ) +
  scale_colour_colorblind()
```
- Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.
```{r}
ggplot(
  data=penguins,
  mapping=aes(x=flipper_length_mm, y=body_mass_g, color=island)
) +
  geom_point() +
  geom_smooth(se=FALSE)
```
- Will these two graphs look different? Why/why not?
```{r}
ggplot(
  data = penguins,
  mapping = aes(x = flipper_length_mm, y = body_mass_g)
) +
  geom_point() +
  geom_smooth()
```
```{r}
ggplot() +
  geom_point(
    data = penguins,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)
  ) +
  geom_smooth(
    data = penguins,
    mapping = aes(x = flipper_length_mm, y = body_mass_g)
  )
```
## ggplot2 calls
